\documentclass[]{ayush-gupta-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Ayush}{Gupta}{ \urlstyle{same}\href{https://ayushgupta11.github.io}{ayushgupta11.github.io}\\
\href{mailto:ayush.gupta.1197@gmail.com}{ayush.gupta.1197@gmail.com} | +91-810-950-1628
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.28\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University Institute of Technology, RGPV}
\descript{B.E. in Computer Science}
\location{Jun 2019 | M.P., India}
\location{ Cum. GPA: 8.01 / 10.0 }
\sectionsep

\subsection{Mount Carmel School}
\descript{Senior Secondary Education}
\location{May 2015 | M.P., India}
\location{ Percentage: 88.4 }
\sectionsep

\subsection{Mount Carmel School}
\descript{Higher Secondary Education}
\location{May 2013 | M.P., India}
\location{ Percentage: 81.17 }
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/ayushgupta11}{\bf ayushgupta11} \\
Medium:// \href{https://medium.com/@ayush.gupta.1197}{\bf @ayush.gupta.1197} \\
LinkedIn://  \href{https://www.linkedin.com/in/ayushgupta1197/}{\bf ayushgupta1197} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Coursework}
% \subsection{Graduate}
% Advanced Machine Learning \\
% Open Source Software Engineering \\
% Advanced Interactive Graphics \\
% Compilers + Practicum \\
% Cloud Computing \\
% Evolutionary Computation \\
% Defending Computer Networks \\
% Machine Learning \\
% \sectionsep

% \subsection{Undergraduate}
% Information Retrieval \\
% Operating Systems \\
% Artificial Intelligence + Practicum \\
% Functional Programming \\
% Computer Graphics + Practicum \\
% {\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst 2x) }}} \\
% Unix Tools and Scripting \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\vspace{2mm}
\location{Primary:}
MERN \textbullet{} MEVN \textbullet{} MEAN \\
\vspace{2mm}
\location{Over 10000 lines:}
React.js \textbullet{}   Node.js \textbullet{} Vue.js \textbullet{} Angular 11 \textbullet{} JavaScript \textbullet{} HTML5 \textbullet{} CSS, SASS \\
\vspace{2mm}
\location{Over 5000 lines:}
TypeScript \textbullet{} GraphQL \textbullet{} React Native \textbullet{} \\
\vspace{2mm}
\location{Over 1000 lines:}
MongoDB \textbullet{} MySQL \\
\vspace{2mm}
\location{Familiar:}
Docker \textbullet{} Kubernetes \textbullet{} Firebase \textbullet{} C \textbullet{} C++ \textbullet{} Java \textbullet{} GIT \textbullet{} NGINX
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
Dec'19  & Yearly Award, Netlink\\
Oct'18  & Quarter 3 Award, Netlink\\
Aug'18  & Half Yearly Award, Netlink\\
Aug'15  & Certificate of Merit, IITG \\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.62\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Infosys Ltd.}
\descript{| Specialist Programmer }
\location{Dec 2020 - Present | Pune, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Part of STG Group at Infosys comprises of full-stack engineers.
\item MEAN Stack Professional @Visa, migrating portal from Angular JS to Angular 11 from scratch
\item Involved in architecturing the front end application so as to improve scalability and reusability
\item MERN Stack Professional @Dow Jones
\end{tightemize}
\sectionsep

\runsubsection{Netlink Software Pvt. Ltd.}
\descript{| Software Engineer }
\location{June 2018 – Dec 2020 | Bhopal, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Full Stack Engineer and a part of Product Team, Lumenore at Netlink Software Pvt. Ltd.
\item Led the migration of the whole product from Polymer to React.JS involving 8 applications in the complete product.
\item Involved in the planning for migrating the platform from on-promise server to cloud architecture.
\item Developed express gateway for serving front-end applications on cloud.
\item Developing a component library for sharing generic components within a micro-frontends architecture.
\item Created an event bus for communicating between multiple UI sub-applications within the application.
\item Developed REST-based APIs using Node.js and Mongo DB for the Self-Service tool for creating datasets, models and dashboards.
\item Created a module for Embedding various business objects and dashboards into external applications using iframe.
\end{tightemize}
\sectionsep

\runsubsection{Netlink Software Pvt. Ltd.}
\descript{| Software Engineering Intern }
\location{Jan 2018 – May 2018 | Bhopal, India}
\begin{tightemize}
\item Intern at the Product Team, Lumenore at Netlink Software Pvt. Ltd.
\item Working on Vue.js and Cordova to create hybrid mobile applications.
\item Developed a News App using Vue.js and Cordova which allows user to sign-in with google and explore news blogs from various external sources.
\item Adding native features to the mobile app using Cordova plugins and using firebase to add multiple features.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{CLI for generating Node.js-based Servers}
\descript{| Node.js}
\location{Jan 2021 – Feb 2021}
A CLI application based on Node.js for generating boilerplate for node-js based server. \\
Similar to create-react-app, etc.
\sectionsep

\runsubsection{Facebook Clone App}
\descript{| React.js, Node.js, MongoDB, Websockets }
\location{April 2020 – May 2020}
A Facebook-like application that lets a user login/signup into the system and add posts to its timeline. \\
Project Link: \textbf {\href{https://posts-app-heroku.herokuapp.com/}{https://posts-app-heroku.herokuapp.com}} 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Publications} 
% \renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
% \bibliographystyle{abbrv}
% \bibliography{publications}
% \nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
